---
title: "Basketball Tracking"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r libraries, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(gridExtra)
library(ggthemes)
library(scales)
library(zoo)
library(knitr)
library(kableExtra)
library(RColorBrewer)
library(toOrdinal)
library(shiny)
library(DT)
library(rsconnect)


```


```{r DataReadBasketball ,include=FALSE}
## Read in data
RawBasketballData <- readxl::read_excel("Basketball Stats.xlsx")

## Reset point
BasketballData <- RawBasketballData


## Filtering out extra rows at bottom
BasketballData <- BasketballData %>%
  filter(!is.na(GameNumber))

## Ben was injured and could not continue on 2018-11-10, Game # 17
## Game counts toward Plus Minus but not toward win loss record
NonContestDateAndGameNumber <- c("2018-11-10 - 17")

## Getting the teammate dataset ready
ScoringData <- BasketballData %>%
  mutate(Id = c(1:nrow(BasketballData))) %>%
  select(Id, GameNumber:PointsFor) %>%
  spread(key = Player ,value = PointsFor) %>%
  group_by(GameNumber) %>%
  summarise(Alex = sum(Alex ,na.rm = T)
            ,Andy = sum(Andy ,na.rm = T)
            ,Ben = sum(Ben ,na.rm = T)
            ,Evan = sum(Evan ,na.rm = T)
            ,Jeff = sum(Jeff ,na.rm = T)
            ,Phil = sum(Phil ,na.rm = T)
            ,RoBert = sum(RoBert ,na.rm = T)
            ,Tim = sum(Tim ,na.rm = T)) %>%
  ungroup()

TeammateData <- BasketballData %>%
  left_join(ScoringData ,by = "GameNumber") %>%
  mutate(PlusMinus = PointsFor - PointsAgainst
         ,DateAndGameNumber = str_c(as.Date(Date) ,' - ' ,GameNumber)
         ,Win = ifelse(DateAndGameNumber %in% NonContestDateAndGameNumber ,0 ,as.integer(PointsFor > PointsAgainst))
         ,Loss = ifelse(DateAndGameNumber %in% NonContestDateAndGameNumber ,0 ,as.integer(PointsFor < PointsAgainst))
         ,GameCount = ifelse(DateAndGameNumber %in% NonContestDateAndGameNumber ,0 ,1)
         ,AlexTeammate = ifelse(PointsFor == Alex ,1 ,0)
         ,AndyTeammate = ifelse(PointsFor == Andy ,1 ,0)
         ,BenTeammate = ifelse(PointsFor == Ben ,1 ,0)
         ,EvanTeammate = ifelse(PointsFor == Evan ,1 ,0)
         ,JeffTeammate = ifelse(PointsFor == Jeff ,1 ,0)
         ,PhilTeammate = ifelse(PointsFor == Phil ,1 ,0)
         ,RoBertTeammate = ifelse(PointsFor == RoBert ,1 ,0)
         ,TimTeammate= ifelse(PointsFor == Tim ,1 ,0)
         ,AlexOpponent = ifelse(PointsFor != Alex ,1 ,0)
         ,AndyOpponent = ifelse(PointsFor != Andy ,1 ,0)
         ,BenOpponent = ifelse(PointsFor != Ben ,1 ,0)
         ,EvanOpponent = ifelse(PointsFor != Evan ,1 ,0)
         ,JeffOpponent = ifelse(PointsFor != Jeff ,1 ,0)
         ,PhilOpponent = ifelse(PointsFor != Phil ,1 ,0)
         ,RoBertOpponent = ifelse(PointsFor != RoBert ,1 ,0)
         ,TimOpponent= ifelse(PointsFor != Tim ,1 ,0)         
         ,AlexWins = ifelse(PointsFor == Alex & Win == 1 ,1 ,0)
         ,AndyWins = ifelse(PointsFor == Andy & Win == 1 ,1 ,0)
         ,BenWins = ifelse(PointsFor == Ben & Win == 1 ,1 ,0)
         ,EvanWins = ifelse(PointsFor == Evan & Win == 1 ,1 ,0)
         ,JeffWins = ifelse(PointsFor == Jeff & Win == 1 ,1 ,0)
         ,PhilWins = ifelse(PointsFor == Phil & Win == 1 ,1 ,0)
         ,RoBertWins = ifelse(PointsFor == RoBert & Win == 1 ,1 ,0)
         ,TimWins= ifelse(PointsFor == Tim & Win == 1 ,1 ,0)   
         ,AlexOpponentWins = ifelse(PointsFor != Alex & Win == 1 ,1 ,0)
         ,AndyOpponentWins = ifelse(PointsFor != Andy & Win == 1 ,1 ,0)
         ,BenOpponentWins = ifelse(PointsFor != Ben & Win == 1 ,1 ,0)
         ,EvanOpponentWins = ifelse(PointsFor != Evan & Win == 1 ,1 ,0)
         ,JeffOpponentWins = ifelse(PointsFor != Jeff & Win == 1 ,1 ,0)
         ,PhilOpponentWins = ifelse(PointsFor != Phil & Win == 1 ,1 ,0)
         ,RoBertOpponentWins = ifelse(PointsFor != RoBert & Win == 1 ,1 ,0)
         ,TimOpponentWins= ifelse(PointsFor != Tim & Win == 1 ,1 ,0)           
         ,AlexPlusMinus = ifelse(PointsFor == Alex ,PlusMinus ,0)
         ,AndyPlusMinus = ifelse(PointsFor == Andy ,PlusMinus ,0)
         ,BenPlusMinus = ifelse(PointsFor == Ben ,PlusMinus ,0)
         ,EvanPlusMinus = ifelse(PointsFor == Evan ,PlusMinus ,0)
         ,JeffPlusMinus = ifelse(PointsFor == Jeff ,PlusMinus ,0)
         ,PhilPlusMinus = ifelse(PointsFor == Phil ,PlusMinus ,0)
         ,RoBertPlusMinus = ifelse(PointsFor == RoBert ,PlusMinus ,0)
         ,TimPlusMinus= ifelse(PointsFor == Tim ,PlusMinus ,0)  
         ,AlexOpponentPlusMinus = ifelse(PointsFor != Alex ,PlusMinus ,0)
         ,AndyOpponentPlusMinus = ifelse(PointsFor != Andy ,PlusMinus ,0)
         ,BenOpponentPlusMinus = ifelse(PointsFor != Ben ,PlusMinus ,0)
         ,EvanOpponentPlusMinus = ifelse(PointsFor != Evan ,PlusMinus ,0)
         ,JeffOpponentPlusMinus = ifelse(PointsFor != Jeff ,PlusMinus ,0)
         ,PhilOpponentPlusMinus = ifelse(PointsFor != Phil ,PlusMinus ,0)
         ,RoBertOpponentPlusMinus = ifelse(PointsFor != RoBert ,PlusMinus ,0)
         ,TimOpponentPlusMinus = ifelse(PointsFor != Tim ,PlusMinus ,0)          
         ,AlexGamesInclNonContest = ifelse(PointsFor == Alex ,1 ,0)
         ,AndyGamesInclNonContest = ifelse(PointsFor == Andy ,1 ,0)
         ,BenGamesInclNonContest = ifelse(PointsFor == Ben ,1 ,0)
         ,EvanGamesInclNonContest = ifelse(PointsFor == Evan ,1 ,0)
         ,JeffGamesInclNonContest = ifelse(PointsFor == Jeff ,1 ,0)
         ,PhilGamesInclNonContest = ifelse(PointsFor == Phil ,1 ,0)
         ,RoBertGamesInclNonContest = ifelse(PointsFor == RoBert ,1 ,0)
         ,TimGamesInclNonContest= ifelse(PointsFor == Tim ,1 ,0)   
         ,AlexOpponentGamesInclNonContest = ifelse(PointsFor != Alex ,1 ,0)
         ,AndyOpponentGamesInclNonContest = ifelse(PointsFor != Andy ,1 ,0)
         ,BenOpponentGamesInclNonContest = ifelse(PointsFor != Ben ,1 ,0)
         ,EvanOpponentGamesInclNonContest = ifelse(PointsFor != Evan ,1 ,0)
         ,JeffOpponentGamesInclNonContest = ifelse(PointsFor != Jeff ,1 ,0)
         ,PhilOpponentGamesInclNonContest = ifelse(PointsFor != Phil ,1 ,0)
         ,RoBertOpponentGamesInclNonContest = ifelse(PointsFor != RoBert ,1 ,0)
         ,TimOpponentGamesInclNonContest= ifelse(PointsFor != Tim ,1 ,0)           
         ,AlexGames = ifelse(PointsFor == Alex & GameCount == 1 ,1 ,0)
         ,AndyGames = ifelse(PointsFor == Andy & GameCount == 1 ,1 ,0)
         ,BenGames = ifelse(PointsFor == Ben & GameCount == 1 ,1 ,0)
         ,EvanGames = ifelse(PointsFor == Evan & GameCount == 1 ,1 ,0)
         ,JeffGames = ifelse(PointsFor == Jeff & GameCount == 1 ,1 ,0)
         ,PhilGames = ifelse(PointsFor == Phil & GameCount == 1 ,1 ,0)
         ,RoBertGames = ifelse(PointsFor == RoBert & GameCount == 1 ,1 ,0)
         ,TimGames = ifelse(PointsFor == Tim & GameCount == 1 ,1 ,0)   
         ,AlexOpponentGames = ifelse(PointsFor != Alex & GameCount == 1 ,1 ,0)
         ,AndyOpponentGames = ifelse(PointsFor != Andy & GameCount == 1 ,1 ,0)
         ,BenOpponentGames = ifelse(PointsFor != Ben & GameCount == 1 ,1 ,0)
         ,EvanOpponentGames = ifelse(PointsFor != Evan & GameCount == 1 ,1 ,0)
         ,JeffOpponentGames = ifelse(PointsFor != Jeff & GameCount == 1 ,1 ,0)
         ,PhilOpponentGames = ifelse(PointsFor != Phil & GameCount == 1 ,1 ,0)
         ,RoBertOpponentGames = ifelse(PointsFor != RoBert & GameCount == 1 ,1 ,0)
         ,TimOpponentGames = ifelse(PointsFor != Tim & GameCount == 1 ,1 ,0)           
         ) %>%
  select(GameNumber:PointsAgainst ,PlusMinus:TimOpponentGames)


## Getting the teammate games data into the necessary format for a chart
TeammateChartData <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = sum(AlexTeammate ,na.rm = T)
            ,Andy = sum(AndyTeammate ,na.rm = T)
            ,Ben = sum(BenTeammate ,na.rm = T)
            ,Evan = sum(EvanTeammate ,na.rm = T)
            ,Jeff = sum(JeffTeammate ,na.rm = T)
            ,Phil = sum(PhilTeammate ,na.rm = T)
            ,RoBert = sum(RoBertTeammate ,na.rm = T)
            ,Tim = sum(TimTeammate ,na.rm = T)) %>%
  gather(key = "Teammate" ,value = "Games" ,Alex:Tim) %>%
  filter(Teammate != Player) %>%
  arrange(Player ,desc(Games))

OpponentChartData <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = sum(AlexOpponent ,na.rm = T)
            ,Andy = sum(AndyOpponent ,na.rm = T)
            ,Ben = sum(BenOpponent ,na.rm = T)
            ,Evan = sum(EvanOpponent ,na.rm = T)
            ,Jeff = sum(JeffOpponent ,na.rm = T)
            ,Phil = sum(PhilOpponent ,na.rm = T)
            ,RoBert = sum(RoBertOpponent ,na.rm = T)
            ,Tim = sum(TimOpponent ,na.rm = T)) %>%
  gather(key = "Opponent" ,value = "Games" ,Alex:Tim) %>%
  filter(Opponent != Player) %>%
  arrange(Player ,desc(Games))

## Getting list of Players
PlayerNames <- TeammateChartData %>%
  select(Player) %>%
  unique() 

## Getting Player with best Plus Minus
TopPlusMinusPlayer <- TeammateData %>%
  group_by(Player) %>%
  summarise(PlusMinus = sum(PlusMinus ,na.rm = T)) %>%
  top_n(1 ,wt = PlusMinus) %>%
  select(Player) %>%
  as.character()

## Get the Plus Minus for all players
PlusMinusData <- TeammateData %>%
  group_by(Player) %>%
  summarise(PlusMinus = sum(PlusMinus ,na.rm = T))


## Get the Win Percent for all players
WinPercentData <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = round(sum(AlexWins ,na.rm = T) / sum(AlexGames ,na.rm = T) ,3)
            ,Andy = round(sum(AndyWins ,na.rm = T) / sum(AndyGames ,na.rm = T) ,3)
            ,Ben = round(sum(BenWins ,na.rm = T) / sum(BenGames ,na.rm = T) ,3)
            ,Evan = round(sum(EvanWins ,na.rm = T) / sum(EvanGames ,na.rm = T) ,3)
            ,Jeff = round(sum(JeffWins ,na.rm = T) / sum(JeffGames ,na.rm = T) ,3)
            ,Phil = round(sum(PhilWins ,na.rm = T) / sum(PhilGames ,na.rm = T) ,3)
            ,RoBert = round(sum(RoBertWins ,na.rm = T) / sum(RoBertGames ,na.rm = T) ,3)
            ,Tim = round(sum(TimWins ,na.rm = T) / sum(TimGames ,na.rm = T) ,3)) %>%
  gather(key = "Teammate" ,value = "WinPercent" ,Alex:Tim) %>%
  filter(Teammate != Player) %>%
  arrange(Player ,desc(WinPercent))

OpponentWinPercentData <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = round(sum(AlexOpponentWins ,na.rm = T) / sum(AlexOpponentGames ,na.rm = T) ,3)
            ,Andy = round(sum(AndyOpponentWins ,na.rm = T) / sum(AndyOpponentGames ,na.rm = T) ,3)
            ,Ben = round(sum(BenOpponentWins ,na.rm = T) / sum(BenOpponentGames ,na.rm = T) ,3)
            ,Evan = round(sum(EvanOpponentWins ,na.rm = T) / sum(EvanOpponentGames ,na.rm = T) ,3)
            ,Jeff = round(sum(JeffOpponentWins ,na.rm = T) / sum(JeffOpponentGames ,na.rm = T) ,3)
            ,Phil = round(sum(PhilOpponentWins ,na.rm = T) / sum(PhilOpponentGames ,na.rm = T) ,3)
            ,RoBert = round(sum(RoBertOpponentWins ,na.rm = T) / sum(RoBertOpponentGames ,na.rm = T) ,3)
            ,Tim = round(sum(TimOpponentWins ,na.rm = T) / sum(TimOpponentGames ,na.rm = T) ,3)) %>%
  gather(key = "Opponent" ,value = "WinPercent" ,Alex:Tim) %>%
  filter(Opponent != Player) %>%
  arrange(Player ,desc(WinPercent))

## Get the Win Percent by Player
WinPercentByPlayer <- TeammateData %>%
  group_by(Player) %>%
  summarise(PlayerWinPercent = round(sum(Win ,na.rm = T) / sum(GameCount ,na.rm = T) ,3))
  
## Get cumulative Plus Minus Data by Player
CumulativePlusMinusData <- TeammateData %>%
  group_by(Player) %>%
  mutate(CumSum = cumsum(PlusMinus)) 

## Getting max & min plus minus across all players for chart
MaxCumulativePlusMinus <- CumulativePlusMinusData %>%
  ungroup() %>%
  summarise(max(CumSum)) %>%
  as.integer()

MinCumulativePlusMinus <- CumulativePlusMinusData %>%
  ungroup() %>%
  summarise(min(CumSum)) %>%
  as.integer()

## Getting the Plus Minus per games by Teammate & Opponent
PlusMinusByTeammate <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = round(sum(AlexPlusMinus ,na.rm = T) / sum(AlexGamesInclNonContest ,na.rm = T) ,3)
            ,Andy = round(sum(AndyPlusMinus ,na.rm = T) / sum(AndyGamesInclNonContest ,na.rm = T) ,3)
            ,Ben = round(sum(BenPlusMinus ,na.rm = T) / sum(BenGamesInclNonContest ,na.rm = T) ,3)
            ,Evan = round(sum(EvanPlusMinus ,na.rm = T) / sum(EvanGamesInclNonContest ,na.rm = T) ,3)
            ,Jeff = round(sum(JeffPlusMinus ,na.rm = T) / sum(JeffGamesInclNonContest ,na.rm = T) ,3)
            ,Phil = round(sum(PhilPlusMinus ,na.rm = T) / sum(PhilGamesInclNonContest ,na.rm = T) ,3)
            ,RoBert = round(sum(RoBertPlusMinus ,na.rm = T) / sum(RoBertGamesInclNonContest ,na.rm = T) ,3)
            ,Tim = round(sum(TimPlusMinus ,na.rm = T) / sum(TimGamesInclNonContest ,na.rm = T) ,3)) %>%
  gather(key = "Teammate" ,value = "PlusMinus" ,Alex:Tim) %>%
  filter(Teammate != Player) %>%
  arrange(Player ,desc(PlusMinus))

PlusMinusByOpponent <- TeammateData %>%
  group_by(Player) %>%
  summarise(Alex = round(sum(AlexOpponentPlusMinus ,na.rm = T) / sum(AlexOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Andy = round(sum(AndyOpponentPlusMinus ,na.rm = T) / sum(AndyOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Ben = round(sum(BenOpponentPlusMinus ,na.rm = T) / sum(BenOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Evan = round(sum(EvanOpponentPlusMinus ,na.rm = T) / sum(EvanOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Jeff = round(sum(JeffOpponentPlusMinus ,na.rm = T) / sum(JeffOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Phil = round(sum(PhilOpponentPlusMinus ,na.rm = T) / sum(PhilOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,RoBert = round(sum(RoBertOpponentPlusMinus ,na.rm = T) / sum(RoBertOpponentGamesInclNonContest ,na.rm = T) ,3)
            ,Tim = round(sum(TimOpponentPlusMinus ,na.rm = T) / sum(TimOpponentGamesInclNonContest ,na.rm = T) ,3)) %>%
  gather(key = "Opponent" ,value = "PlusMinus" ,Alex:Tim) %>%
  filter(Opponent != Player) %>%
  arrange(Player ,desc(PlusMinus))

## Getting max & min plus minus by teammate / opponent for chart
MaxTeammatePlusMinus <- PlusMinusByTeammate %>%
  ungroup() %>%
  summarise(max(PlusMinus)) %>%
  as.numeric()

MinTeammatePlusMinus <- PlusMinusByTeammate %>%
  ungroup() %>%
  summarise(min(PlusMinus)) %>%
  as.numeric()

MaxOpponentPlusMinus <- PlusMinusByOpponent %>%
  ungroup() %>%
  summarise(max(PlusMinus)) %>%
  as.numeric()

MinOpponentPlusMinus <- PlusMinusByOpponent %>%
  ungroup() %>%
  summarise(min(PlusMinus)) %>%
  as.numeric()

## Getting data for static Plus Minus chart
CurrentPlusMinus <- TeammateData %>%
  group_by(Player) %>%
  summarise(PlusMinus = sum(PlusMinus))

PlusMinusLevels <- CurrentPlusMinus %>%
  arrange(PlusMinus ,desc(Player)) %>%
  select(Player) %>%
  unlist()

CurrentPlusMinus$Player <- factor(CurrentPlusMinus$Player ,levels = PlusMinusLevels)

## Getting max & min plus minus by game 
PlusMinusByGame <- CumulativePlusMinusData %>%
  ungroup() %>%
  group_by(GameNumber) %>%
  summarise(MaxPlusMinus = max(CumSum)
            ,MinPlusMinus = min(CumSum)) 

## Adding the max / min plus minus by game to the original dataset
CumulativePlusMinusData <- CumulativePlusMinusData %>%
  left_join(PlusMinusByGame ,by = "GameNumber") %>%
  mutate(King = ifelse(CumSum == MaxPlusMinus ,1 ,0)
        ,Bottom = ifelse(CumSum == MinPlusMinus ,1 ,0))

## Weeks as King or at Bottom
WeeksAsKing <- CumulativePlusMinusData %>%
  filter(GameNumber > 10) %>%
  group_by(Player) %>%
  summarise(WeeksAsKing = sum(King ,na.rm = T)
            ,WeeksAtBottom = sum(Bottom ,na.rm = T))

MaxWeeksAsKing <- WeeksAsKing %>%
  ungroup() %>%
  summarise(max(WeeksAsKing)) %>%
  as.numeric()

MaxWeeksAtBottom <- WeeksAsKing %>%
  ungroup() %>%
  summarise(max(WeeksAtBottom)) %>%
  as.numeric()

  

```


```{r MarchMadness ,include=FALSE}
RawMarchMadness <- readxl::read_excel("March Madness.xlsx" ,sheet = "Data")

## Reset point
MarchMadness <- RawMarchMadness

## Remove spaces in column names
OriginalColumnNames <- colnames(MarchMadness)
colnames(MarchMadness) <- str_replace_all(colnames(MarchMadness) ,pattern = ' ' ,replacement = '')

## Getting the slider ranges
MinYear <- MarchMadness %>%
  summarise(MinYear = min(YEAR)) %>%
  as.integer()

MaxYear <- MarchMadness %>%
  summarise(MaxYear = max(YEAR)) %>%
  as.integer()

## Putting into chart format
PointsChart <- MarchMadness %>%
  select(YEAR:NCG) %>%
  gather(key = "Round", value = "Points" ,R64:NCG)

PicksChart <- MarchMadness %>%
  select(YEAR:PLAYER ,R64Correct:NCGCorrect) %>%
  gather(key = "Round", value = "Points" ,R64Correct:NCGCorrect)

PicksChart <- PicksChart %>%  
  mutate(Round = str_sub(Round ,start = 1 ,end = str_length(Round) - 7)) 

## Factor for rounds
RoundLevels <- c("R64" ,"R32" ,"S16" ,"E8" ,"F4" ,"NCG")
PointsChart$Round <- factor(PointsChart$Round ,levels = RoundLevels)
PicksChart$Round <- factor(PicksChart$Round ,levels = RoundLevels)


## Getting data for a summary table
Champion <- MarchMadness %>%
  filter(RANK == 1) %>%
  mutate(Champion = str_c(PLAYER ,' (' ,BRACKETNAME ,' - ' ,prettyNum(TOTAL ,big.mark = ',') ,' points)')) %>%
  select(YEAR ,Champion)

MostPicks <- MarchMadness %>%
  group_by(YEAR) %>%
  arrange(desc(TotalCorrect) ,desc(TOTAL) ,PLAYER) %>%
  top_n(1) %>%
  mutate(MostCorrect = str_c(PLAYER ,' - ' ,TotalCorrect ,' picks')) %>%
  select(YEAR ,MostCorrect)

LeastPicks <- MarchMadness %>%
  group_by(YEAR) %>%
  arrange(TotalCorrect ,TOTAL ,PLAYER) %>%
  top_n(-1) %>%
  mutate(LeastCorrect = str_c(PLAYER ,' - ' ,TotalCorrect ,' picks')) %>%
  select(YEAR ,LeastCorrect)

WorstRankByYear <- MarchMadness %>%
  group_by(YEAR) %>%
  summarise(WorstRank = max(RANK))

LeastPoints <- MarchMadness %>%
  inner_join(WorstRankByYear ,by = c("YEAR" ,"RANK" = "WorstRank")) %>%
  mutate(LeastPoints = str_c(PLAYER ,' - ' ,prettyNum(TOTAL ,big.mark = ',') ,' points')) %>%
  select(YEAR ,LeastPoints)

CorrectChampions <- MarchMadness %>%
  group_by(YEAR) %>%
  summarise(CorrectChampionPicks = sum(NCGCorrect))

SummaryTable <- Champion %>%
  left_join(LeastPoints ,by = "YEAR") %>%
  left_join(MostPicks ,by = "YEAR") %>%
  left_join(LeastPicks ,by = "YEAR") %>%
  left_join(CorrectChampions ,by = "YEAR") 

colnames(SummaryTable) <- c("Year" ,"Champion" ,"Lowest Scorer" ,"Most Correct Picks" ,"Least Correct Picks" ,"Total Correct Champion Picks")

```


Player Performance by Teammate {data-navmenu="Basketball Tracking"}
=======================================================================

Column {data-width=200 .sidebar}
-----------------------------------------------------------------------
```{r}

selectInput("PlayerInput"
            ,"Select a player:"
            ,choices = PlayerNames$Player
            ,selected = TopPlusMinusPlayer)

```



Column {data-width=450}
-----------------------------------------------------------------------

### Current Plus Minus

```{r}

ReactivePlusMinusData <- reactive({
  PlusMinusData %>%
    filter(Player == input$PlayerInput)
})

renderValueBox(
  valueBox(ReactivePlusMinusData() %>% select(PlusMinus)
           ,icon = "fa-arrows-v"
           ,color = ifelse(ReactivePlusMinusData() %>% select(PlusMinus) > 5, "success", ifelse(ReactivePlusMinusData() %>% select(PlusMinus) > -6 ,"warning" ,"danger")))
)


```

### Plus Minus per game by Teammate

```{r}

ReactivePlusMinusByTeammate <- reactive({
  PlusMinusByTeammate %>%
    filter(Player == input$PlayerInput)
})


renderPlot({
  ggplot(ReactivePlusMinusByTeammate() ,aes(x = reorder(Teammate ,PlusMinus ,function(x) {x}) ,y = PlusMinus ,fill = PlusMinus)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(limits = c(MinTeammatePlusMinus ,MaxTeammatePlusMinus)) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen") ,limit = c(MinTeammatePlusMinus ,MaxTeammatePlusMinus)) +    
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()      
})

```


### Plus Minus Over Time 

```{r}

ReactiveCumulativePlusMinusData <- reactive({
  CumulativePlusMinusData %>%
    filter(Player == input$PlayerInput)
})


renderPlot({
  ggplot(ReactiveCumulativePlusMinusData() ,aes(x = GameNumber ,y = CumSum ,fill = CumSum)) +
    geom_col() +
    scale_y_continuous(limits = c(MinCumulativePlusMinus ,MaxCumulativePlusMinus)) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Game Number" ,fill = "Plus Minus") +
    # scale_fill_brewer(palette = "Set1") +
    scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen") ,limit = c(MinCumulativePlusMinus ,MaxCumulativePlusMinus)) +
    theme_fivethirtyeight()    
})



```


Column {data-width=350}
-----------------------------------------------------------------------

### Player Win Percent 

```{r}

ReactiveWinPercent <- reactive({
  WinPercentByPlayer %>%
    filter(Player == input$PlayerInput) %>%
    mutate(PlayerWinPercent2 = PlayerWinPercent * 100) %>%
    select(PlayerWinPercent2) %>%
    unique() %>%
    as.numeric()
})

renderGauge({
  gauge(ReactiveWinPercent() 
        ,min = 0 
        ,max = 100 
        ,symbol = '%'
        ,sectors = gaugeSectors(success = c(55 ,100) ,warning = c(45 ,54.9) ,danger = c(0 ,44.9)))
})


```


### Win Percent by Teammate

```{r}

ReactiveWinPercentData <- reactive({
  WinPercentData %>%
    left_join(WinPercentByPlayer ,by = "Player") %>%
    # mutate(Color = ifelse(PlayerWinPercent > .55 ,"green" ,ifelse(PlayerWinPercent > .45 ,"yellow" ,"red"))) %>%
    filter(Player == input$PlayerInput)
})

ReactivePlayerWinPercentData <- reactive({
  WinPercentByPlayer %>%
    filter(Player == input$PlayerInput)
})

renderPlot({
  ggplot(ReactiveWinPercentData() ,aes(x = reorder(Teammate ,WinPercent ,function(x) {x}) ,y = WinPercent)) +
    geom_col() +
    geom_hline(yintercept = ReactiveWinPercentData() %>% select(PlayerWinPercent) %>% unique() %>% as.numeric() 
               # ,color = ReactiveWinPercentData() %>% select(Color) %>% unique() %>% as.character()
               ) +
    coord_flip() +
    scale_y_continuous(limits = c(0 ,1) ,labels = scales::percent) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()    
})

```


### Games Played with Teammate

```{r}

ReactiveTeammateChartData <- reactive({
  TeammateChartData %>%
    filter(Player == input$PlayerInput)
})

renderPlot({
  ggplot(ReactiveTeammateChartData() ,aes(x = reorder(Teammate ,Games ,function(x) {x}) ,y = Games)) +
    geom_col() +
    coord_flip() +
    # scale_y_continuous(labels = scales::pretty_breaks) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()    
})


```


Rivalry Corner {data-navmenu="Basketball Tracking"}
=======================================================================

Column {data-width=200 .sidebar}
-----------------------------------------------------------------------
```{r}

selectInput("PlayerInput2"
            ,"Select a player:"
            ,choices = PlayerNames$Player
            ,selected = TopPlusMinusPlayer)

```

Column {data-width=450}
-----------------------------------------------------------------------

### Longest Win Streak

```{r}

ReactiveLongestWinStreak <- reactive({
  TeammateData %>%
    filter(Player == input$PlayerInput2 & !(DateAndGameNumber %in% NonContestDateAndGameNumber)) %>%
    summarise(LongestWinStreak2 = max(rle(Win == 1)[[1]][rle(Win == 1)[[2]] == 1])) %>%
    as.numeric()
})


renderValueBox(
  valueBox(ReactiveLongestWinStreak()
           ,color = ifelse(ReactiveLongestWinStreak() < 3 ,"danger" ,ifelse(ReactiveLongestWinStreak() < 5  ,"warning" ,"success")))
)

```


### Plus Minus per game against Opponent

```{r}

ReactivePlusMinusByOpponent <- reactive({
  PlusMinusByOpponent %>%
    filter(Player == input$PlayerInput2)
})


renderPlot({
  ggplot(ReactivePlusMinusByOpponent() ,aes(x = reorder(Opponent ,PlusMinus ,function(x) {x}) ,y = PlusMinus ,fill = PlusMinus)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(limits = c(MinOpponentPlusMinus ,MaxOpponentPlusMinus)) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen") ,limit = c(MinOpponentPlusMinus ,MaxOpponentPlusMinus)) +    
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()      
})

```


Column {data-width=350}
-----------------------------------------------------------------------

### Current Win Streak

```{r}
ReactiveCurrentWinStreak <- reactive({
  TeammateData %>%  
    filter(Player == input$PlayerInput2 & !(DateAndGameNumber %in% NonContestDateAndGameNumber)) %>%
    select(Win) %>%
    summarise(Current = ifelse(rle(Win)$values[length(rle(Win)$values)] == 0 ,0 ,rle(Win)$lengths[length(rle(Win)$lengths)])) %>%
    as.numeric()
})


renderValueBox(
  valueBox(ReactiveCurrentWinStreak()
           ,color = ifelse(ReactiveCurrentWinStreak() == 0, "danger" ,ifelse(ReactiveCurrentWinStreak() < 4  ,"warning" ,"success")))
)



```


### Win Percent against Opponent

```{r}

ReactiveOpponentWinPercentData <- reactive({
  OpponentWinPercentData %>%
    left_join(WinPercentByPlayer ,by = "Player") %>%
    # mutate(Color = ifelse(PlayerWinPercent > .55 ,"green" ,ifelse(PlayerWinPercent > .45 ,"yellow" ,"red"))) %>%
    filter(Player == input$PlayerInput2)
})


renderPlot({
  ggplot(ReactiveOpponentWinPercentData() ,aes(x = reorder(Opponent ,WinPercent ,function(x) {x}) ,y = WinPercent)) +
    geom_col() +
    geom_hline(yintercept = ReactiveOpponentWinPercentData() %>% select(PlayerWinPercent) %>% unique() %>% as.numeric() 
               # ,color = ReactiveWinPercentData() %>% select(Color) %>% unique() %>% as.character()
               ) +
    coord_flip() +
    scale_y_continuous(limits = c(0 ,1) ,labels = scales::percent) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()    
})

```


### Games Played against Opponent

```{r}

ReactiveOpponentChartData <- reactive({
  OpponentChartData %>%
    filter(Player == input$PlayerInput2)
})

renderPlot({
  ggplot(ReactiveOpponentChartData() ,aes(x = reorder(Opponent ,Games ,function(x) {x}) ,y = Games)) +
    geom_col() +
    coord_flip() +
    # scale_y_continuous(labels = scales::pretty_breaks) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()    
})


```


Cross Player Comparisons {data-navmenu="Basketball Tracking"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Weeks as King

```{r}

renderPlot({
  ggplot(WeeksAsKing ,aes(x = reorder(Player ,WeeksAsKing ,function(x) {x}) ,y = WeeksAsKing ,fill = WeeksAsKing)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(limits = c(0 ,MaxWeeksAsKing)) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen") ,limit = c(0 ,MaxWeeksAsKing)) +    
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()      
})

```

### Weeks at Bottom

```{r}

renderPlot({
ggplot(WeeksAsKing ,aes(x = reorder(Player ,WeeksAtBottom ,function(x) {x}) ,y = WeeksAtBottom ,fill = WeeksAtBottom)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(limits = c(0 ,MaxWeeksAtBottom)) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    scale_fill_gradientn(colors = c("darkgreen", "palegreen","tomato1", "darkred") ,limit = c(0 ,MaxWeeksAtBottom)) +    
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()      
})

```

Column {data-width=500}
-----------------------------------------------------------------------

### Current Plus Minus Comparison

```{r}

renderPlot({
ggplot(CurrentPlusMinus ,aes(x = Player ,y = PlusMinus ,fill = PlusMinus)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_gradient(low = "indianred", high = "forestgreen") +
  scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen")) +
  theme_fivethirtyeight()
})

```

### Current Win Percent Comparison

```{r}

renderPlot({
  ggplot(WinPercentByPlayer ,aes(x = reorder(Player ,PlayerWinPercent ,function(x) {x}) ,y = PlayerWinPercent)) +
    geom_col() +
    geom_hline(yintercept = .5) +
    coord_flip() +
    scale_y_continuous(limits = c(0 ,1) ,labels = scales::percent) +
    # scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen")) +
    # ggtitle("Points by Player") +
    # theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Player") +
    # scale_fill_brewer(palette = "Set1") +
    theme_fivethirtyeight()   
})

```


March Madness
=======================================================================

Column {data-width=200 .sidebar}
-----------------------------------------------------------------------
```{r Sidebar}

sliderInput("YearSlider", 
            label = "Select years to display:",
            min = MinYear, 
            max = MaxYear, 
            value = c(MinYear,MaxYear), 
            step = 1L)

checkboxGroupInput("RoundCheckbox", 
                   h3("Checkbox group"), 
                   choices = as.list(RoundLevels),
                   # choices = list("Choice 1" = 1, 
                   #                "Choice 2" = 2, 
                   #                "Choice 3" = 3),
                   selected = as.list(RoundLevels))


```


Column {data-width=450}
-----------------------------------------------------------------------

### Total Points by Player

```{r}

ReactivePointsChart <- reactive({
  PointsChart %>%
    filter(YEAR %in% input$YearSlider & Round %in% input$RoundCheckbox) 
    # filter(YEAR <= input$YearSlider[1] & YEAR >= input$YearSlider[2] & Round %in% input$RoundCheckbox) 
})

renderPlot({
ggplot(ReactivePointsChart() ,aes(x = reorder(PLAYER, Points, function(x){ sum(x) } ),y = Points ,fill = as.factor(YEAR))) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = scales::comma) +
  # ggtitle("Points by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Player" ,fill = "Year") +
  scale_fill_brewer(palette = "Set1") +
  theme_fivethirtyeight()  
})

 

```

Column {data-width=350}
-----------------------------------------------------------------------

### Correct Picks by Player

```{r}

ReactivePicksChart <- reactive({
  PicksChart %>%
    filter(YEAR %in% input$YearSlider & Round %in% input$RoundCheckbox) 
})

renderPlot({
ggplot(ReactivePicksChart() ,aes(x = reorder(PLAYER, Points, function(x){ sum(x) } ),y = Points ,fill = as.factor(YEAR))) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = scales::comma) +
  # ggtitle("Picks by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Player" ,fill = "Year") +
  scale_fill_brewer(palette = "Set1") +
  theme_fivethirtyeight()  
})



```

### Summary Table

```{r}

datatable(SummaryTable ,rownames = FALSE)

```




















