---
title: "Basketball Stats"
author: "RoBert Riesenberg"
output: html_document
---

```{r libraries, include=FALSE}
library(tidyverse)
library(gridExtra)
library(ggthemes)
library(scales)
```

## Summary

The purpose of this document is to track the performance of players who come to play basketball on the weekends. It will be updated each week soon after our games. This earliest games recorded are as of September 23rd, 2018. 

## Record by Player

The records by player are as follows:

```{r Record,echo=FALSE ,warning=FALSE}

BasketballData <- readxl::read_excel("C:\\Users\\riese\\Desktop\\Basketball\\Basketball Stats.xlsx")

## Ben was injured and could not continue on 2018-11-10, Game # 17
NonContestDateAndGameNumber <- c("2018-11-10 - 17")

## This code adds in Sean & Josh into the template
# BasketballDataOtherPlayers <- data.frame(GameNumber = c(22 ,23 ,24 ,22 ,23 ,24) ,Date = c("2018-11-25" ,"2018-11-25" ,"2018-11-25" ,"2018-11-25" ,"2018-11-25" ,"2018-11-25") ,Player = c("Sean" ,"Sean" ,"Sean" ,"Josh" ,"Josh" ,"Josh") ,PointsFor = c(11 ,15, 16 ,15 ,13 ,14) ,PointsAgainst = c(15 ,13 ,14 ,11 ,15 ,16))
# 
# BasketballDataOtherPlayers$Date <- as.POSIXct(BasketballDataOtherPlayers$Date)
# BasketballDataOtherPlayers$Player <- as.character(BasketballDataOtherPlayers$Player)
# 
# BasketballData <- BasketballData %>%
#   bind_rows(BasketballDataOtherPlayers)

TwelveGamePlayers <- BasketballData %>%
  group_by(Player) %>%
  summarise(GamesPlayed = n()) %>%
  filter(GamesPlayed > 12) %>%
  select(Player) %>%
  unlist()

BasketballData <- BasketballData %>%
  mutate(DateAndGameNumber = str_c(as.Date(Date) ,' - ' ,GameNumber)
         ,Win = ifelse(DateAndGameNumber %in% NonContestDateAndGameNumber ,0 ,as.integer(PointsFor > PointsAgainst))
         ,Loss = ifelse(DateAndGameNumber %in% NonContestDateAndGameNumber ,0 ,as.integer(PointsFor < PointsAgainst))
         ,PlusMinus = PointsFor - PointsAgainst
         ,Month = lubridate::month(Date ,label = T ,abbr = T)
         ,Year = lubridate::year(Date)
         ,MonthYear = str_c(lubridate::month(Date ,label = T ,abbr = T), ' - ', lubridate::year(Date))
         ,YearMonth = str_c(lubridate::year(Date), ' - ', lubridate::month(Date ,label = T ,abbr = F))) %>%
  filter(complete.cases(BasketballData))

BasketballDataTidyRecord <- BasketballData %>%
  gather(key = "WinType" ,value = "WinIndicator" ,Win ,Loss) 

BasketballDataTidyRecordSum <- BasketballDataTidyRecord %>%
  group_by(Player ,WinType) %>%
  summarise(Record = sum(WinIndicator)
            ,Losses = sum())

RecordLevels <- BasketballDataTidyRecordSum %>%
  filter(WinType == "Win") %>%
  arrange(Record ,desc(Player)) %>%
  select(Player) %>%
  unlist()

BasketballDataTidyRecordSum$Player <- factor(BasketballDataTidyRecordSum$Player ,levels = RecordLevels)

ggplot(BasketballDataTidyRecordSum ,aes(x = Player ,y = Record ,fill = WinType)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  ggtitle("Total Wins by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette = "Set1") +
  theme_fivethirtyeight() +
  scale_y_continuous(breaks= pretty_breaks())


```

Win percentage by player:

```{r WinPercent ,echo=FALSE ,warning=FALSE}

ggplot(BasketballDataTidyRecordSum %>% filter(Player %in% TwelveGamePlayers) ,aes(x = Player ,y = Record ,fill = WinType)) +
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  ggtitle("Win Percentage by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette = "Set1") +
  theme_fivethirtyeight()

```


## Total Points by Player

The total points for & against are as follows:

```{r TotalPoints,echo=FALSE ,warning=FALSE}
### Add in a chart that counts the number of games by month as time goes on ###
# ggplot(BasketballData %>% group_by(MonthYear) %>% summarise(n = n_distinct(GameNumber)), aes(x = MonthYear ,y = n ,group = 1)) +
#   geom_bar(stat = "identity")

### Add in a chart that counts the number of games by player & month as time goes on ###
# ggplot(BasketballData %>% group_by(MonthYear ,Player) %>% summarise(n = n_distinct(GameNumber)), aes(x = Player ,y = n)) +
#   geom_bar(stat = "identity") +
#   facet_wrap(~MonthYear) +
#   coord_flip()

BasketballDataTidy <- BasketballData %>%
  gather(key = "PointsType" ,value = "Points" ,PointsAgainst ,PointsFor)

BasketballDataTidySum <- BasketballDataTidy %>%
  group_by(Player, PointsType) %>%
  summarise(Points = sum(Points)
            ,PlusMinus = sum(PlusMinus))

PointsLevels <- BasketballDataTidySum %>%
  filter(PointsType == "PointsFor") %>%
  arrange(Points ,desc(Player)) %>%
  select(Player) %>%
  unlist()

BasketballDataTidySum$Player <- factor(BasketballDataTidySum$Player ,levels = PointsLevels)

ggplot(BasketballDataTidySum ,aes(x = Player ,y = Points ,fill = PointsType)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  ggtitle("Points For And Points Against by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette = "Dark2" ,direction = -1) +
  theme_fivethirtyeight()

```

## Plus Minus by Player

Here is the plus minus broken out by Player.

```{r PlusMinus, echo=FALSE}

BasketballDataPlusMinus <- BasketballData %>%
  group_by(Player) %>%
  summarise(PlusMinus = sum(PlusMinus))

PlusMinusLevels <- BasketballDataPlusMinus %>%
  arrange(PlusMinus ,desc(Player)) %>%
  select(Player) %>%
  unlist()

BasketballDataPlusMinus$Player <- factor(BasketballDataPlusMinus$Player ,levels = PlusMinusLevels)

ggplot(BasketballDataPlusMinus %>% filter(Player %in% TwelveGamePlayers) ,aes(x = Player ,y = PlusMinus ,fill = PlusMinus)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ggtitle("Plus Minus by Player") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_gradient(low = "indianred", high = "forestgreen") +
  scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen")) +
  theme_fivethirtyeight()

```

## Plus Minus by Player & Date

The plus minus broken out over time by Player.

```{r PlusMinusByMonth, echo=FALSE}
 
BasketballDataPlusMinusByDate <- BasketballData %>%
  group_by(Date, Player) %>%
  summarise(PlusMinus = sum(PlusMinus))

PlusMinusLevelsByDate <- BasketballDataPlusMinus %>%
  arrange(desc(PlusMinus) ,desc(Player)) %>%
  select(Player) %>%
  unlist()

BasketballDataPlusMinusByDate$Player <- factor(BasketballDataPlusMinusByDate$Player ,levels = PlusMinusLevelsByDate)

## set width ~ 450,000 when more players get added into this chart
ggplot(BasketballDataPlusMinusByDate %>% filter(Player %in% TwelveGamePlayers) ,aes(x = Date ,y = PlusMinus ,fill = PlusMinus)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Player) +
  # geom_text(aes(label = PlusMinus) ,position = position_dodge(width = 1) ,size = 2 ,vjust = "inward") +
  ggtitle("Plus Minus by Player & Date") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_gradient(low = "indianred", high = "forestgreen") +
  scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen")) +
  theme_fivethirtyeight() +
  theme(legend.position="none" ,axis.text.x=element_text(angle=45,hjust=1))
  

```

## Games Played over Time

The total number of games played over time are as follows. Note that games which end early due to injury are not included.

```{r GamesOverTime ,echo = FALSE ,warning=FALSE}

BasketballDataOverTime <- BasketballData %>%
  filter(!(DateAndGameNumber %in% NonContestDateAndGameNumber) & (Player %in% TwelveGamePlayers)) %>%
  group_by(Date) %>%
  summarise(GamesPlayed = n_distinct(GameNumber ,Date))

## set width ~ 450,000 when more players get added into this chart
ggplot(BasketballDataOverTime ,aes(x = Date ,y = GamesPlayed)) +
  geom_bar(stat = "identity" ,fill = "#4B0082") +
  ggtitle("Games Played Over Time") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_fivethirtyeight()
  
```


## Future Charts 

These charts will be created as more time / games elapse: 

* Plus Minus per Game Played
* Games Played by Player
* Record by Player & Month
